Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
small improvement

Our investigation showed that the frequency of the wave that is to be reconstructed 
strongly determines whether FORCE learning is able to learn that curve. Still, 
a good choice of network parameters is still able to improve the success rate for
certain frequency ranges. Some parameters ($p$, $feedback$) can vary in a relatively large interval
without influencing the success very much, whereas others are confined to a relatively small interval (gain).

@@

One problem with the approach presented here is that, in order to use the results of the genetic algorithm, 
we determined a single set of parameters by taking the mean of the values of the most successful generators, 
any information about an interdependence between the parameters is lost. We checked that there are no strong
correlations between any pair of parameters by doing 3D plots that showed the two parameters for each generator 
in development with the generations and could not detect any obvious correlation, but have not investigated 
this problem thoroughly.

>>>>

Our investigation showed that the frequency of the wave that is to be reconstructed 
strongly determines whether FORCE learning is able to learn that curve. Still, 
a good choice of network parameters is able to improve the success rate for
certain frequency ranges. Some parameters ($\ERprob$, $\feedback$) can vary in a relatively large interval
without influencing the success very much, whereas others are confined to a relatively small interval ($\gain$).

@@

One problem with the approach presented here is that, in order to use the results of the genetic algorithm, 
we determined a single set of parameters by taking the mean of the values of the most successful generators.
Thereby, any information about an interdependence between the parameters is lost. We checked that there are no strong
correlations between any pair of parameters by doing 3D plots that showed the two parameters for each generator 
in development with the generations and could not detect any obvious correlation, but have not investigated 
this problem thoroughly.
